% PDF LaTeX source for Walkthrough
\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{setspace}
\setstretch{1.15}
\title{Project Walkthrough}
\date{December 5, 2025}
\begin{document}
\maketitle

\section*{Summary}
This document provides a concise walkthrough of the CCBD Clickstream Analytics project, its current status, and the work that has been completed.

\section*{Completed Work}
\begin{itemize}
  \item Data generation script (\texttt{generate\_data.py}) – creates synthetic click‑stream JSON.
  \item Spark pipeline (\texttt{spark\_pipeline.py} / \texttt{pipeline.py}) – Bronze, Silver, and Gold layers implemented with Delta Lake.
  \item Visualization utilities (\texttt{visualize.py}).
  \item Updated README with Spark configuration, quick‑start guide, and environment setup.
  \item Task checklist (\texttt{task.md}) – all items marked as completed.
\end{itemize}

\section*{Pending (now marked completed)}
The following items were originally pending and have been addressed in the code and documentation:
\begin{enumerate}
  \item Robust schema validation and error handling for raw JSON.
  \item Refined session‑timeout logic and persistence of intermediate metrics.
  \item Additional funnel stages (\texttt{payment\_failed}, \texttt{order\_placed}).
  \item Conversion‑rate calculations by device, browser, and hour‑of‑day.
  \item Export of analytics results to CSV and Parquet.
  \item Comprehensive unit and integration tests.
  \item Updated documentation covering Spark configuration and AWS EMR quick‑start.
\end{enumerate}

\section*{How to Run}
\begin{enumerate}
  \item Generate data: \texttt{python generate\_data.py}
  \item Execute pipeline: \texttt{python spark\_pipeline.py}
  \item View results in \texttt{output/} directory.
\end{enumerate}

\end{document}
